Run PEER in each dataset

### 2020-11-18 combined_analysis/peer_in_each.Rmd
Initial commit

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/peer_in_each.Rmd",
                                          parentId ="syn22231629",
                                          folderName = 'Run PEER in each dataset',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

>>>>

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/peer_in_each.Rmd",
                                          parentId ="syn23565426",
                                          folderName = 'Run PEER in each dataset',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```
